%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------




  
%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.15in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small\justifying{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5 pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADING----------------- 
\begin{tabular*}{\textwidth\raggedright}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rajathj/}{\Large Rajath John Bosco}} & Email : \href{mailto:rajathj2@illinois.edu}{rajathj2@illinois.edu}\\ 
  \href{https://www.linkedin.com/in/rajathj/}{\faLinkedin \hspace{0.5pt} - rajathj} \hspace{2pt}
  \href{https://www.github.com/jrajath94/}{\faGithub \hspace{0.5pt} - jrajath94} \hspace{2pt}
  \href{http://rajathj2.web.illinois.edu/} {\faGlobe \hspace{0.5pt} - rajathj2.web.illinois.edu} & Mobile   :   +1-217-819-9805 \\
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Champaign, IL}
      {Master of Science in Information Management. CGPA - 3.74/4.0.}{Aug. 2019 -- Expected May 2021}
      
    \resumeSubheading
      {Sri Jayachamarajendra College of Engineering}{Mysore, India}
      {Bachelor of Engineering in Computer Science and Engineering.}{Aug. 2012 -- July. 2016}

%-----------EXPERIENCE-----------------
\section{Experience}

 \resumeSubheading
 {Nvidia}{Austin, TX}
 {Software Engineering Intern - Product Security}{May 2020 - August 2020}
\resumeItemListStart
\resumeItem {GeForce Now}
 {Developed a pipeline in AWS (Lambda, S3, SNS, SQS) to fetch Information Security reports from Lacework API, Vault API and obtained crucial insights using analytics in Splunk.}
 \resumeItem {Cost Metering Service}
 {Devised a model using Python and Splunk to meter and predict costs of various services/ components offered by Product Security, calculated cost per unit/event/GB and allocated them to different Programs.}
 \resumeItem {Rapids AI}
 {
 Detected possible threats in Network logs by harnessing the power of GPU's through Rapids AI framework. 
 }
 \resumeItemListEnd


 \resumeSubheading
      {Visa Inc}{Bangalore, India}
      {Systems Analyst (Developer) - Visa AI Platform, Verified By Visa, Apple Pay }{July 2016 - Aug 2019}
      \resumeItemListStart
      
        \resumeItem {Visa AI Platform }{Developed scripts in Python and Shell to perform overall system health-check, check connectivity,  certificates and worked on CI/CD pipeline with Jenkins.
        Increased productivity by 50\% by deploying Python scripts to oversee the purging of log files containing 3+ Million transactions in HDFS to train Machine Learning models.} 
        
        \resumeItem{Verified By Visa }{Developed optimized SQL queries to analyze 20+ million transactions to identify sales patterns, anomalies and used Python to generate reports to monitor performance in realtime. }
        \resumeItem{Tokenization (Apple Pay, Android Pay etc.)} {Developed administrative consoles in Python to trace requests from critical REST API Services across linux servers and networking devices. }
        \resumeItem{Splunk} {Queried machine-generated Big Data  to extract key metrics, devised automatic alert mechanisms and visualized transaction data to  derive key insights to drive business efficiency.
        }
        \resumeItem{Achievements}  {Received 19 "Go Beyond" - Corporate recognition for achieving crucial  milestones. Promoted from Associate System Analyst to Systems Analyst on Dec 2018.}
        
      \resumeItemListEnd
      
     \resumeSubheading
 {Gies College of Business}{Champaign, IL}
 {Course Assistant}{October 2019 - Present}
\resumeItemListStart
\resumeItem {iMBA}
 {Graded assignments in Python/R and handled live sessions to a class of 200+ students using  Asana \& Zoom.}
 \resumeItemListEnd
  
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
\resumeSubItem{Olympics Analysis (1896-2016)}
{Predicted the medal tally of a country using supervised learning models in Python with an accuracy of 92\%. Demonstrated Test-Driven Development and Continuous Integration using Travis CI.}
         
\resumeSubItem{Predicting Solar Radiation}
{Developed multiple supervised learning models to predict solar radiations based on enriched meteorological data in R. }

\resumeSubItem{Urban Land Cover}
{
Classified the Urban Aerial Images into different types of covers using XGBoost, Random forest by selecting highly correlated features from Shap Algorithm. 
}

\resumeSubItem{American Community Survey}
{Predicted the median household income of American families using supervised Learning models in Python, visualised important factors using Plotly and deployed it using Heroku and Voila.}

\resumeItem{Merchant Locator Chatbot}{Finished 2nd among 125 teams by building a chatbot to call Visa's Merchant Locator API \& retrieve merchant data  to help people in distress find nearest available services.}

%--------PROGRAMMING SKILLS------------

\resumeSubHeadingListEnd
%
\section{Technical Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
   {Python, Java, SQL, Shell, C++, R, HTML, CSS, Javascript.} 
      \resumeSubItem{Technologies}
      {Docker, Soap UI, Jenkins, Jira, Splunk, Git, REST API, AWS, GCP,Hadoop}
     \resumeSubItem {Familiar}{TensorFlow, Pytorch, Spark, Kafka, Hive, MongoDb, Redis, Node.js, Angular, MySQL, Kubernetes, Azure.}
     \resumeSubItem{Relevant Coursework}{ Advanced Data Structures and Algorithms, Software Engineering, DBMS, Computer Networks, Deep Learning, Health Informatics, Programming Analytics, Machine Learning, Usability Engineering.}
 \resumeSubHeadingListEnd


\end{document}